---
title: "Triple_results"
author: "Xuewei Han"
date: "3/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(mlr)
library(randomForest)
library(FSelectorRcpp)
library(FSelector)
library(ggpubr)

library(ggplot2)
library(dplyr)
library(PerformanceAnalytics)

setwd("/Users/xueweihan/OneDrive - University of Southern California/Biostats/thesis/missing feature models")
```


### READ DATA

```{r}
HepG2Z <- read.delim("HepG2Z")
HepG2Z$gene <- as.factor(HepG2Z$gene)
HepG2Z$truelink <- factor(HepG2Z$truelink, levels = 0:1)

K562Z <- read.delim("K562Z")
K562Z$gene <- as.factor(K562Z$gene)
K562Z$truelink <- factor(K562Z$truelink, levels = 0:1)

MCF7Z <- read.delim("MCF7Z")
MCF7Z$gene <- as.factor(MCF7Z$gene)
MCF7Z$truelink <- factor(MCF7Z$truelink, levels = 0:1)

HCT116Z <- read.delim("HCT116Z")
HCT116Z$gene <- as.factor(HCT116Z$gene)
HCT116Z$truelink <- factor(HCT116Z$truelink, levels = 0:1)

tripleZ <- read.delim("tripleZ")
tripleZ$gene <- as.factor(tripleZ$gene)
tripleZ$truelink <- factor(tripleZ$truelink, levels = 0:1)

HepG2_K562Z <- read.delim("HepG2_K562Z")
HepG2_K562Z$gene <- as.factor(HepG2_K562Z$gene)
HepG2_K562Z$truelink <- factor(HepG2_K562Z$truelink, levels = 0:1)

HepG2_HCT116Z <- read.delim("HepG2_HCT116Z")
HepG2_HCT116Z$gene <- as.factor(HepG2_HCT116Z$gene)
HepG2_HCT116Z$truelink <- factor(HepG2_HCT116Z$truelink, levels = 0:1)

K562_HCT116Z <- read.delim("K562_HCT116Z")
K562_HCT116Z$gene <- as.factor(K562_HCT116Z$gene)
K562_HCT116Z$truelink <- factor(K562_HCT116Z$truelink, levels = 0:1)

```

### Feature Engineering

## univariate analysis for triple
```{r}
triple <- read.delim("triplev1")
#creating interaction variables
triple$H3K27ac_H3K4me1 <- (triple$H3K27ac_enhancer)*(triple$H3K4me1)
triple$H3K27ac_H3K4me3 <- (triple$H3K27ac_enhancer)*(triple$H3K4me3)
triple$H3K27ac_promoterH3K27ac <- (triple$H3K27ac_enhancer)*(triple$H3K27ac_promoter)
triple$H3K4me1_H3K4me3 <- (triple$H3K4me1)*(triple$H3K4me3)
triple$H3K4me1_promoterH3K27ac <- (triple$H3K27ac_promoter)*(triple$H3K4me1)
triple$eQTL_eQTL_coeff_abs <- (triple$eQTL_Zscore)*(triple$coeff_abs)
triple$H3K27ac_H3K4me1_H3K4me3 <- (triple$H3K27ac_enhancer)*(triple$H3K4me1)*(triple$H3K4me3)
triple$H3K27ac_promoterH3K27ac_H3K4me1 <- (triple$H3K27ac_enhancer)*(triple$H3K27ac_promoter)*(triple$H3K4me1)

#adjust feature format
triple$truelink <- factor(triple$truelink)
triple$gene <- factor(triple$gene)
triple$H3K27ac_enhancer <- as.factor(triple$H3K27ac_enhancer)
triple$H3K4me1 <- as.numeric(triple$H3K4me1)
triple$H3K4me3 <- as.factor(triple$H3K4me3)
triple$eQTL_Zscore <- as.numeric(triple$eQTL_Zscore)
triple$nearest <- as.factor(triple$nearest)
triple$intronic_target <- as.factor(triple$intronic_target)
triple$coeff_abs <- as.numeric(triple$coeff_abs)
triple$H3K27ac_promoter <- as.numeric(triple$H3K27ac_promoter)

summarizeColumns(triple)

#plot the connection with truelink and features
par(mfrow=c(3,3))
for(i in c("H3K4me1","eQTL_Zscore", "coeff_abs", "H3K27ac_promoter")){
 plot(triple$truelink, triple[, i],cex=1, ylab=i, xlab="TrueLinks", main=paste("TrueLinks v.s.", i))
}
for(i in c("H3K27ac_enhancer","H3K4me3", "nearest", "intronic_target")){
 plot(triple$truelink, triple[, i], cex=1, xlab="TrueLinks", ylab=i, main=paste("TrueLinks v.s.", i))
}

#distribution of numeric features
par(mfrow=c(3,2))
for(i in c("H3K4me1","eQTL_Zscore", "coeff_abs", "H3K27ac_promoter")){
 hist(triple[, i],cex=1, ylab="..", xlab=i, main=paste("Distribution of", i))
}

#chi-square tests for binary features
chisq.test(table(triple$H3K27ac_enhancer, triple$truelink))
chisq.test(table(triple$H3K4me3, triple$truelink)) #not significant
chisq.test(table(triple$nearest, triple$truelink))
chisq.test(table(triple$intronic_target, triple$truelink))

#correlation analysis
corr <- cor(triple[c("H3K4me1","eQTL_Zscore", "coeff_abs", "H3K27ac_promoter")])
round(corr,2)

my_data <- triple[c("H3K4me1","eQTL_Zscore", "coeff_abs", "H3K27ac_promoter")]
chart.Correlation(my_data, histogram=TRUE, pch=19)
```

## how to create *Z
```{r}
#standardizing variables
tripleZ <- triple[11]
#if blocking by gene or enhancer (otherwise skip)
tripleZ$gene <- as.factor(triple$gene)

tripleZ$H3K4me1 <- ((triple$H3K4me1-mean(triple$H3K4me1))/sd(triple$H3K4me1))
tripleZ$eQTL_Zscore <- ((triple$eQTL_Zscore-mean(triple$eQTL_Zscore))/sd(triple$eQTL_Zscore))
tripleZ$coeff_abs <- ((triple$coeff_abs-mean(triple$coeff_abs))/sd(triple$coeff_abs))
tripleZ$H3K27ac_promoter <- ((triple$H3K27ac_promoter-mean(triple$H3K27ac_promoter))/sd(triple$H3K27ac_promoter))

tripleZ$H3K27ac_enhancer <- triple$H3K27ac_enhancer
tripleZ$H3K4me3 <- triple$H3K4me3
tripleZ$nearest <- triple$nearest
tripleZ$intronic_target <- triple$intronic
tripleZ$truelink <- factor(tripleZ$truelink, levels = 0:1)

#creating interaction variables
tripleZ$H3K27ac_H3K4me1 <- (tripleZ$H3K27ac_enhancer)*(tripleZ$H3K4me1)
tripleZ$H3K27ac_H3K4me3 <- (tripleZ$H3K27ac_enhancer)*(tripleZ$H3K4me3)
tripleZ$H3K27ac_promoterH3K27ac <- (tripleZ$H3K27ac_enhancer)*(tripleZ$H3K27ac_promoter)
tripleZ$H3K4me1_H3K4me3 <- (tripleZ$H3K4me1)*(tripleZ$H3K4me3)
tripleZ$H3K4me1_promoterH3K27ac <- (tripleZ$H3K27ac_promoter)*(tripleZ$H3K4me1)
tripleZ$eQTL_eQTL_coeff_abs <- (tripleZ$eQTL_Zscore)*(tripleZ$coeff_abs)
tripleZ$H3K27ac_H3K4me1_H3K4me3 <- (tripleZ$H3K27ac_enhancer)*(tripleZ$H3K4me1)*(tripleZ$H3K4me3)
tripleZ$H3K27ac_promoterH3K27ac_H3K4me1 <- (tripleZ$H3K27ac_enhancer)*(tripleZ$H3K27ac_promoter)*(tripleZ$H3K4me1)

summarizeColumns(tripleZ)

#write.table(tripleZ, file = "tripleZ", sep = "\t", row.names = FALSE, quote = FALSE)

#tripleZ <- read.delim("tripleZ")
#summarizeColumns(tripleZ)
```


### Machine Learning Models

## Balanced Random Forest without blockings

```{r}
triple_tsk <- makeClassifTask(id = "Enhancer-Gene Links", data = tripleZ[-2,], target = "truelink")

triple_tsk <- dropFeatures(triple_tsk, features = c("gene")); triple_tsk

rdesc <- makeResampleDesc("RepCV", reps=30L, folds = 3L)

#random forest

rfbal.lrn <- makeLearner("classif.randomForest", fix.factors.prediction = TRUE,
                        predict.type = "prob", par.vals = list(classwt=c(0.84,0.16), importance=TRUE))

#repeated cross validation

set.seed(242) 
r <- resample(learner = rfbal.lrn, task = triple_tsk, resampling = rdesc, measures = auc, show.info = FALSE)

r$aggr #0.9093
```

## Add Blockings

```{r}
triple_tsk <- makeClassifTask(id = "Enhancer-Gene Links", data = tripleZ, target = "truelink", blocking = factor(tripleZ$gene), positive = 1)

triple_tsk <- dropFeatures(triple_tsk, features = c("gene")); triple_tsk

rdesc <- makeResampleDesc("RepCV", reps=30L, folds = 3L, blocking.cv=T)

rfbal.lrn <- makeLearner("classif.randomForest", fix.factors.prediction = TRUE,
                        predict.type = "prob", par.vals = list(classwt=c(0.84,0.16), importance=TRUE))

#repeated cross validation

set.seed(242) 
r <- resample(learner = rfbal.lrn, task = triple_tsk, resampling = rdesc, measures = auc, show.info = FALSE)

r$aggr #0.8828948

boxplot(r$measures.test$auc, main=paste('RF AUCs from 30 repeats of 3-fold CV (gene blocking)\nMean AUC:',round(r$aggr[[1]],digits=4)), xlab='triple')


#test in other cell lines

set.seed(242)
triple_rfbal <- train(rfbal.lrn, triple_tsk)

triple_predict_HepG2 <- predict(triple_rfbal, newdata = HepG2Z)
auc_test <- performance(triple_predict_HepG2, measures = auc); auc_test #0.9483772

triple_predict_K562 <- predict(triple_rfbal, newdata = K562Z)
auc_test <- performance(triple_predict_K562, measures = auc); auc_test #0.7282708

triple_predict_MCF7 <- predict(triple_rfbal, newdata = MCF7Z)
auc_test <- performance(triple_predict_MCF7, measures = auc); auc_test #0.8691358

triple_predict_HCT116 <- predict(triple_rfbal, newdata = HCT116Z)
auc_test <- performance(triple_predict_HCT116, measures = auc); auc_test #0.8989922
```

### Feature Selection

## filter methods

*Results:*

- "H3K27ac_H3K4me1", *Mean AUC=0.7166685*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", *Mean AUC=0.7421482*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", *Mean AUC=0.7541204*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", *Mean AUC=0.8315692*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", *Mean AUC=0.8653692*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", *Mean AUC=0.8614732*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", *Mean AUC=0.8686303*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K27ac_enhancer", *Mean AUC=0.8680887*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K27ac_enhancer", "intronic_target", *Mean AUC=0.8643499*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K27ac_enhancer", "intronic_target", "H3K4me1_promoterH3K27ac", *Mean AUC=0.8623368*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K27ac_enhancer", "intronic_target", "H3K4me1_promoterH3K27ac", "H3K27ac_H3K4me3", *Mean AUC=0.8622063*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K27ac_enhancer", "intronic_target", "H3K4me1_promoterH3K27ac", "H3K27ac_H3K4me3", "eQTL_Zscore", *Mean AUC=0.8879639* *!!!*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K27ac_enhancer", "intronic_target", "H3K4me1_promoterH3K27ac", "H3K27ac_H3K4me3", "eQTL_Zscore", "coeff_abs", *Mean AUC=0.8880892*

- "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K27ac_enhancer", "intronic_target", "H3K4me1_promoterH3K27ac", "H3K27ac_H3K4me3", "eQTL_Zscore", "coeff_abs", "eQTL_eQTL_coeff_abs", *Mean AUC=0.8886065*

- full model, *Mean AUC=0.8799706*

# calculating the feature importance
```{r}

#method1
fv = generateFilterValuesData(triple_tsk, method = "FSelector_information.gain")
fv$data

plotFilterValues(fv)

fv$data[which(value >0)][order(value, decreasing = TRUE)]
fv$data[which(value >0)][order(value, decreasing = TRUE)]$name
```
*List of features with importance>0: (14)*

"H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K27ac_enhancer", "intronic_target", "H3K4me1_promoterH3K27ac", "H3K27ac_H3K4me3", "eQTL_Zscore", "coeff_abs", "eQTL_eQTL_coeff_abs"      

*List of full features:*
"H3K4me1", "eQTL_Zscore", "coeff_abs", "H3K27ac_promoter", "H3K27ac_enhancer", "H3K4me3", "nearest", "intronic_target", "H3K27ac_H3K4me1", "H3K27ac_H3K4me3", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K4me1_promoterH3K27ac", "eQTL_eQTL_coeff_abs", "H3K27ac_H3K4me1_H3K4me3", "H3K27ac_promoterH3K27ac_H3K4me1"


# Selecting a feature subset
```{r}
filtered.task = filterFeatures(triple_tsk, fval = fv, threshold =0.01)
filtered.task # "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest", "H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K27ac_enhancer", "intronic_target", "H3K4me1_promoterH3K27ac", "H3K27ac_H3K4me3", "eQTL_Zscore", "coeff_abs", "eQTL_eQTL_coeff_abs"   
set.seed(242)
r = resample(learner = rfbal.lrn, task = filtered.task, resampling = rdesc, measures = auc, show.info = FALSE)
r$aggr #0.8886065

filtered.task = filterFeatures(triple_tsk, fval = fv, perc = 0.25)
filtered.task # "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac_H3K4me1", "H3K27ac_H3K4me1_H3K4me3", "nearest"
set.seed(242)
r = resample(learner = rfbal.lrn, task = filtered.task, resampling = rdesc, measures = auc, show.info = FALSE)
r$aggr #0.8315692


# first eight features
triple_tsk_drop = dropFeatures(triple_tsk, features = c("eQTL_Zscore", "coeff_abs", "H3K27ac_promoter", "H3K4me3", "intronic_target", "H3K27ac_H3K4me3", "H3K4me1_promoterH3K27ac", "eQTL_eQTL_coeff_abs"))
set.seed(242) 
r = resample(learner = rfbal.lrn, task = triple_tsk_drop, resampling = rdesc, measures = auc, show.info = FALSE)
print(paste("Mean AUC :", round(r$aggr,digits=7)))

#test in other cell lines
set.seed(242)
triple_rfbal = train(rfbal.lrn, triple_tsk_drop)

triple_predict_HepG2 <- predict(triple_rfbal, newdata = HepG2Z)
auc_test <- performance(triple_predict_HepG2, measures = auc); auc_test

triple_predict_K562 <- predict(triple_rfbal, newdata = K562Z)
auc_test <- performance(triple_predict_K562, measures = auc); auc_test

triple_predict_MCF7 <- predict(triple_rfbal, newdata = MCF7Z)
auc_test <- performance(triple_predict_MCF7, measures = auc); auc_test

triple_predict_HCT116 <- predict(triple_rfbal, newdata = HCT116Z)
auc_test <- performance(triple_predict_HCT116, measures = auc); auc_test
```

# Fuse a learner with a filter method
```{r}
lrn = makeFilterWrapper(learner = "classif.randomForest", fw.method ="FSelector_information.gain", fw.abs = 2)
r = resample(learner = lrn, task = triple_tsk, resampling =rdesc, show.info = FALSE, models = TRUE)
r$aggr
sfeats = sapply(r$models, getFilteredFeatures)
table(sfeats)

#               H3K27ac_H3K4me1         H3K27ac_H3K4me1_H3K4me3         H3K27ac_promoterH3K27ac H3K27ac_promoterH3K27ac_H3K4me1 
#                             62                              13                              18                              33 
#                        H3K4me1                 H3K4me1_H3K4me3                 intronic_target                         nearest 
#                             17                               7                               2                              28 
```
# Tuning the size of the feature subset
```{r}
lrn = makeFilterWrapper(learner = "classif.randomForest", fw.method ="FSelector_information.gain")
ps = makeParamSet(makeDiscreteParam("fw.perc", values = seq(0.2,0.5, 0.05)))
res = tuneParams(lrn, task = triple_tsk, resampling = rdesc,par.set = ps,control = makeTuneControlGrid())

as.data.frame(res$opt.path)

lrn = makeFilterWrapper(learner = "classif.randomForest", fw.method ="FSelector_information.gain", fw.perc = res$x$fw.perc)
mod = train(lrn, triple_tsk)
getFilteredFeatures(mod)

# first eight
# "H3K4me1", "H3K27ac_enhancer", "nearest", "H3K27ac_H3K4me1", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K27ac_H3K4me1_H3K4me3", "H3K27ac_promoterH3K27ac_H3K4me1"
```
## Wrapper methods

# Select a feature subset
```{r}
### Specify the search strategy
ctrl = makeFeatSelControlRandom(maxit = 17L)
ctrl

### Resample description
#rdesc = makeResampleDesc("Holdout")
### Select features
sfeats = selectFeatures(learner = "classif.randomForest", task =triple_tsk, resampling = rdesc, control = ctrl, show.info = FALSE)
sfeats
sfeats$x
#[1] "H3K27ac_enhancerZ"                "eQTL_Zscore_Z"                    "coeff_abs_Z"                     
#[4] "H3K27ac_promoterZ"                "p300Z"                            "nearest"                         
#[7] "H3K27ac_H3K4me1Z"                 "H3K27ac_H3K4me1_H3K4me3Z"         "H3K27ac_promoterH3K27ac_H3K4me1Z"
sfeats$y
#0.06985424

### Specify the search strategy
ctrl = makeFeatSelControlSequential(method = "sfs", alpha = 0.02)
### Select features
sfeats = selectFeatures(learner = "classif.randomForest", task = triple_tsk, resampling = rdesc, control = ctrl,show.info = FALSE)
sfeats
analyzeFeatSelResult(sfeats)


```

# Fuse a learner with feature selection
```{r}
lrn = makeFeatSelWrapper("classif.randomForest", resampling = rdesc,control = makeFeatSelControlRandom(maxit = 10), show.info =
FALSE)
mod = train(lrn, task = triple_tsk)
mod

sfeats = getFeatSelResult(mod)
sfeats

sfeats$x

r = resample(learner = lrn, task = triple_tsk, resampling =rdesc, models = TRUE,show.info = FALSE)
r$aggr
lapply(r$models, getFeatSelResult)
```


### Drop One Feature

```{r}
#feature list: "H3K4me1", "eQTL_Zscore", "coeff_abs", "H3K27ac_promoter", "H3K27ac_enhancer", "H3K4me3", "nearest", "intronic_target", "H3K27ac_H3K4me1", "H3K27ac_H3K4me3", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K4me1_promoterH3K27ac", "eQTL_eQTL_coeff_abs", "H3K27ac_H3K4me1_H3K4me3", "H3K27ac_promoterH3K27ac_H3K4me1"

for(i in c("H3K4me1", "eQTL_Zscore", "coeff_abs", "H3K27ac_promoter", "H3K27ac_enhancer", "H3K4me3", "nearest", "intronic_target", "H3K27ac_H3K4me1", "H3K27ac_H3K4me3", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K4me1_promoterH3K27ac", "eQTL_eQTL_coeff_abs", "H3K27ac_H3K4me1_H3K4me3", "H3K27ac_promoterH3K27ac_H3K4me1")){
  triple_tsk_drop = dropFeatures(triple_tsk, features = c(i))
  set.seed(242) 
  r = resample(learner = rfbal.lrn, task = triple_tsk_drop, resampling = rdesc, measures = auc, show.info = FALSE)
  print(paste("Mean AUC if dropping", i, ":", round(r$aggr,digits=4)))
  
  set.seed(242)
  triple_rfbal = train(rfbal.lrn, triple_tsk_drop)

  triple_predict = predict(triple_rfbal, newdata = HepG2Z)
  auc_test = performance(triple_predict, measures = auc); auc_test 
  print(paste("AUC in HepG2:", round(auc_test,digits=4)))
  
  triple_predict = predict(triple_rfbal, newdata = K562Z)
  auc_test = performance(triple_predict, measures = auc); auc_test
  print(paste("AUC in K562:", round(auc_test,digits=4)))

  triple_predict2 = predict(triple_rfbal, newdata = MCF7Z)
  auc_test = performance(triple_predict2, measures = auc); auc_test
  print(paste("AUC in MCF7:", round(auc_test,digits=4)))
  
  triple_predict2 = predict(triple_rfbal, newdata = HCT116Z)
  auc_test = performance(triple_predict2, measures = auc); auc_test
  print(paste("AUC in HCT116:", round(auc_test,digits=4)))
}



```
*Results with validation in HepG2, K562, MCF7, and HCT116*
[1] "Mean AUC if dropping H3K4me1 : 0.8816"
[1] "AUC in HepG2: 0.9448"
[1] "AUC in K562: 0.7531"
[1] "AUC in MCF7: 0.8649"
[1] "AUC in HCT116: 0.8836"
[1] "Mean AUC if dropping eQTL_Zscore : 0.8816"
[1] "AUC in HepG2: 0.9186"
[1] "AUC in K562: 0.7215"
[1] "AUC in MCF7: 0.8682"
[1] "AUC in HCT116: 0.8879"
[1] "Mean AUC if dropping coeff_abs : 0.8848"
[1] "AUC in HepG2: 0.9468"
[1] "AUC in K562: 0.79"
[1] "AUC in MCF7: 0.8546"
[1] "AUC in HCT116: 0.9059"
[1] "Mean AUC if dropping H3K27ac_promoter : 0.8888"
[1] "AUC in HepG2: 0.9411"
[1] "AUC in K562: 0.7287"
[1] "AUC in MCF7: 0.8836"
[1] "AUC in HCT116: 0.909"
[1] "Mean AUC if dropping H3K27ac_enhancer : 0.8833"
[1] "AUC in HepG2: 0.946"
[1] "AUC in K562: 0.7395"
[1] "AUC in MCF7: 0.8662"
[1] "AUC in HCT116: 0.8993"
[1] "Mean AUC if dropping H3K4me3 : 0.8853"
[1] "AUC in HepG2: 0.9478"
[1] "AUC in K562: 0.7295"
[1] "AUC in MCF7: 0.8688"
[1] "AUC in HCT116: 0.9025"
[1] "Mean AUC if dropping nearest : 0.866"
[1] "AUC in HepG2: 0.915"
[1] "AUC in K562: 0.7405"
[1] "AUC in MCF7: 0.8174"
[1] "AUC in HCT116: 0.8965"
[1] "Mean AUC if dropping intronic_target : 0.8821"
[1] "AUC in HepG2: 0.9451"
[1] "AUC in K562: 0.7286"
[1] "AUC in MCF7: 0.9148"
[1] "AUC in HCT116: 0.8935"
[1] "Mean AUC if dropping H3K27ac_H3K4me1 : 0.8832"
[1] "AUC in HepG2: 0.9461"
[1] "AUC in K562: 0.746"
[1] "AUC in MCF7: 0.8687"
[1] "AUC in HCT116: 0.8968"
[1] "Mean AUC if dropping H3K27ac_H3K4me3 : 0.886"
[1] "AUC in HepG2: 0.946"
[1] "AUC in K562: 0.7363"
[1] "AUC in MCF7: 0.8625"
[1] "AUC in HCT116: 0.8927"
[1] "Mean AUC if dropping H3K27ac_promoterH3K27ac : 0.8843"
[1] "AUC in HepG2: 0.9461"
[1] "AUC in K562: 0.7276"
[1] "AUC in MCF7: 0.8632"
[1] "AUC in HCT116: 0.9052"
[1] "Mean AUC if dropping H3K4me1_H3K4me3 : 0.8826"
[1] "AUC in HepG2: 0.9404"
[1] "AUC in K562: 0.7515"
[1] "AUC in MCF7: 0.8666"
[1] "AUC in HCT116: 0.8902"
[1] "Mean AUC if dropping H3K4me1_promoterH3K27ac : 0.8902"
[1] "AUC in HepG2: 0.9482"
[1] "AUC in K562: 0.7303"
[1] "AUC in MCF7: 0.8762"
[1] "AUC in HCT116: 0.8828"
[1] "Mean AUC if dropping eQTL_eQTL_coeff_abs : 0.8847"
[1] "AUC in HepG2: 0.9444"
[1] "AUC in K562: 0.7252"
[1] "AUC in MCF7: 0.8639"
[1] "AUC in HCT116: 0.8961"
[1] "Mean AUC if dropping H3K27ac_H3K4me1_H3K4me3 : 0.8848"
[1] "AUC in HepG2: 0.944"
[1] "AUC in K562: 0.7614"
[1] "AUC in MCF7: 0.8748"
[1] "AUC in HCT116: 0.9007"
[1] "Mean AUC if dropping H3K27ac_promoterH3K27ac_H3K4me1 : 0.8875"
[1] "AUC in HepG2: 0.9453"
[1] "AUC in K562: 0.7281"
[1] "AUC in MCF7: 0.8624"
[1] "AUC in HCT116: 0.8962"


### Only include one feature

```{r}
feature_name = names(tripleZ)[-c(1,6)]
feature_name

for(i in c("H3K4me1", "eQTL_Zscore", "coeff_abs", "H3K27ac_promoter", "H3K27ac_enhancer", "H3K4me3", "nearest", "intronic_target", "H3K27ac_H3K4me1", "H3K27ac_H3K4me3", "H3K27ac_promoterH3K27ac", "H3K4me1_H3K4me3", "H3K4me1_promoterH3K27ac", "eQTL_eQTL_coeff_abs", "H3K27ac_H3K4me1_H3K4me3", "H3K27ac_promoterH3K27ac_H3K4me1")){
  triple_tsk_drop = dropFeatures(triple_tsk, features = feature_name[feature_name != i])
  set.seed(242) 
  r = resample(learner = rfbal.lrn, task = triple_tsk_drop, resampling = rdesc, measures = auc, show.info = FALSE)
  print(paste("Mean AUC if only including", i, ":", round(r$aggr,digits=4)))
  
  set.seed(242)
  triple_rfbal = train(rfbal.lrn, triple_tsk_drop)

  triple_predict = predict(triple_rfbal, newdata = HepG2Z)
  auc_test = performance(triple_predict, measures = auc); auc_test
  print(paste("AUC in HepG2:", round(auc_test,digits=4)))
  
  triple_predict = predict(triple_rfbal, newdata = K562Z)
  auc_test = performance(triple_predict, measures = auc); auc_test
  print(paste("AUC in K562:", round(auc_test,digits=4)))

  triple_predict2 = predict(triple_rfbal, newdata = MCF7Z)
  auc_test = performance(triple_predict2, measures = auc); auc_test
  print(paste("AUC in MCF7:", round(auc_test,digits=4)))
  
  triple_predict2 = predict(triple_rfbal, newdata = HCT116Z)
  auc_test = performance(triple_predict2, measures = auc); auc_test
  print(paste("AUC in HCT116:", round(auc_test,digits=4)))
}

```

*Results:*
[1] "Mean AUC if only including H3K4me1 : 0.7492" *!!!*
[1] "AUC in HepG2: 0.6659"
[1] "AUC in K562: 0.6145"
[1] "AUC in MCF7: 0.6505"
[1] "AUC in HCT116: 0.7875"
[1] "Mean AUC if only including eQTL_Zscore : 0.5871"
[1] "AUC in HepG2: 0.5639"
[1] "AUC in K562: 0.6733"
[1] "AUC in MCF7: 0.5872"
[1] "AUC in HCT116: 0.6207"
[1] "Mean AUC if only including coeff_abs : 0.6053"
[1] "AUC in HepG2: 0.5869"
[1] "AUC in K562: 0.5565"
[1] "AUC in MCF7: 0.5262"
[1] "AUC in HCT116: 0.6197"
[1] "Mean AUC if only including H3K27ac_promoter : 0.4975"
[1] "AUC in HepG2: 0.4483"
[1] "AUC in K562: 0.4472"
[1] "AUC in MCF7: 0.5014"
[1] "AUC in HCT116: 0.4618"
[1] "Mean AUC if only including H3K27ac_enhancer : 0.624"
[1] "AUC in HepG2: 0.5"
[1] "AUC in K562: 0.5"
[1] "AUC in MCF7: 0.5"
[1] "AUC in HCT116: 0.5"
[1] "Mean AUC if only including H3K4me3 : 0.5"
[1] "AUC in HepG2: 0.5"
[1] "AUC in K562: 0.5"
[1] "AUC in MCF7: 0.5"
[1] "AUC in HCT116: 0.5"
[1] "Mean AUC if only including nearest : 0.6824"
[1] "AUC in HepG2: 0.8154" *!!!*
[1] "AUC in K562: 0.5392"
[1] "AUC in MCF7: 0.7293"
[1] "AUC in HCT116: 0.7291"
[1] "Mean AUC if only including intronic_target : 0.6128"
[1] "AUC in HepG2: 0.684"
[1] "AUC in K562: 0.5167"
[1] "AUC in MCF7: 0.5322"
[1] "AUC in HCT116: 0.6595"
[1] "Mean AUC if only including H3K27ac_H3K4me1 : 0.7167" *!!!*
[1] "AUC in HepG2: 0.6403"
[1] "AUC in K562: 0.6811"
[1] "AUC in MCF7: 0.8452" *!!!*
[1] "AUC in HCT116: 0.7239"
[1] "Mean AUC if only including H3K27ac_H3K4me3 : 0.605"
[1] "AUC in HepG2: 0.5"
[1] "AUC in K562: 0.5"
[1] "AUC in MCF7: 0.5"
[1] "AUC in HCT116: 0.5"
[1] "Mean AUC if only including H3K27ac_promoterH3K27ac : 0.6993"
[1] "AUC in HepG2: 0.7025"
[1] "AUC in K562: 0.7095"
[1] "AUC in MCF7: 0.7625"
[1] "AUC in HCT116: 0.6923"
[1] "Mean AUC if only including H3K4me1_H3K4me3 : 0.709" *!!!*
[1] "AUC in HepG2: 0.6662"
[1] "AUC in K562: 0.5502"
[1] "AUC in MCF7: 0.5217"
[1] "AUC in HCT116: 0.7971"
[1] "Mean AUC if only including H3K4me1_promoterH3K27ac : 0.646"
[1] "AUC in HepG2: 0.5168"
[1] "AUC in K562: 0.5461"
[1] "AUC in MCF7: 0.4678"
[1] "AUC in HCT116: 0.4396"
[1] "Mean AUC if only including eQTL_eQTL_coeff_abs : 0.5722"
[1] "AUC in HepG2: 0.4606"
[1] "AUC in K562: 0.6007"
[1] "AUC in MCF7: 0.4878"
[1] "AUC in HCT116: 0.5719"
[1] "Mean AUC if only including H3K27ac_H3K4me1_H3K4me3 : 0.6841"
[1] "AUC in HepG2: 0.6249"
[1] "AUC in K562: 0.6794"
[1] "AUC in MCF7: 0.6462"
[1] "AUC in HCT116: 0.7129"
[1] "Mean AUC if only including H3K27ac_promoterH3K27ac_H3K4me1 : 0.7214" *!!!*
[1] "AUC in HepG2: 0.6731"
[1] "AUC in K562: 0.6326"
[1] "AUC in MCF7: 0.8173" *!!!*
[1] "AUC in HCT116: 0.6886"




